\documentclass[11pt, a4paper]{article}
\usepackage{cv}

\begin{document}

% ==============================================================================
% CONTACT INFORMATION & TECHNICAL LINKS
% ==============================================================================
\makeheader{Your Name}{
    \contactItem{https://map.location}{\faMapMarker*}{City}{}
    \contactSeparator
    \contactItem{mailto:email@example.com}{\faEnvelope[regular]}{email@example.com}{}
    \contactSeparator
    \contactItem{tel:+1234567890}{\faPhone*}{+1 234 567 890}{}
    \contactSeparator
    \contactItem{https://linkedin.com/in/yourprofile}{\faLinkedinIn}{linkednin.com/in/yourprofile}{}
    \contactSeparator
    \contactItem{https://github.com/yourgithub}{\faGithub}{github.com/yourgithub}{}
}

% ==============================================================================
% TECHNICAL PROFILE / PROFESSIONAL SUMMARY (OPTIONAL)
% ==============================================================================
\section{Technical Profile / Professional Summary}
\cvSummary{Provide a brief 2-3 sentence summary highlighting your core technical skills, research interests, and what you aim to achieve in your academic or professional career.}

% ==============================================================================
% EDUCATION
% ==============================================================================
\section{Education}
\cvEducation
    {University or Institution Name}
    {Degree Name in Major}
    {City, Country}
    {Month, Year – Month, Year}
    {
        \item \textbf{Relevant Coursework:} Course 1, Course 2, Course 3, Course 4
        \item \textbf{Thesis:} Title of your thesis or research focus
    }

% ==============================================================================
% CORE COMPETENCIES & TECHNICAL SKILLS
% ==============================================================================
\section{Core Competencies \& Technical Skills}
\cvSkill{Programming Languages}{Skill 1, Skill 2, Skill 3, Skill 4, Skill 5}
\cvSkill{Frameworks \& Libraries}{Skill 1, Skill 2, Skill 3, Skill 4, Skill 5}
\cvSkill{Tools \& Technologies}{Skill 1, Skill 2, Skill 3, Skill 4, Skill 5}

% ==============================================================================
% TECHNICAL PROJECTS / RESEARCH EXPERIENCE
% ==============================================================================
\section{Technical Projects / Research Experience}
\cvProject
    {Research or Project Title}
    {Technology 1, Technology 2}
    {Month, Year – Month, Year}
    {Research Lab or Project Type}
    {
        \item Action verb + what you researched or built + how you did it + quantifiable outcome.
        \item Highlight specific methodologies, algorithms, or technical problems solved.
    }

% ==============================================================================
% PROFESSIONAL EXPERIENCE / INTERNSHIPS (OPTIONAL)
% ==============================================================================
\section{Professional Experience / Internships}

\cvExperience
    {Role Title}
    {Technology 1, Technology 2, Technology 3}
    {Month, Year – Present}
    {Company / Organization}
    {
        \item Action verb + what you did + how you did it + quantifiable result or impact.
        \item Highlight a specific technical implementation detail or problem solved.
        \item Another bullet point highlighting a key contribution or feature.
    }

% ==============================================================================
% PUBLICATIONS & PRESENTATIONS (OPTIONAL)
% ==============================================================================
\section{Publications \& Presentations}

\cvPublication
    {Title of the Publication or Presentation}
    {\textbf{Your Name}, Co-author 1, Co-author 2}
    {Name of the Journal or Conference}
    {Month, Year}
    {https://doi.org/10.xxxx/xxxxx}
    {DOI/Link}

% ==============================================================================
% AWARDS, HONORS & CERTIFICATIONS (OPTIONAL)
% ==============================================================================
\section{Awards, Honors \& Certifications}

\cvCert
    {Award or Certification Name}
    {Month, Year}
    {https://link-to-credential.com}
    {Issuing Organization / Verify Credential}

% ==============================================================================
% EXTRACURRICULAR ACTIVITIES / LEADERSHIP (OPTIONAL)
% ==============================================================================
\section{Extracurricular Activities / Leadership}

\cvExperience
    {Leadership Role or Position Title}
    {Event or Sub-group}
    {Month, Year – Month, Year}
    {Club / Organization}
    {
        \item Describe your involvement, leadership responsibilities, and achievements.
        \item Highlight specific initiatives you led or events organized.
    }

% ==============================================================================
% REFERENCES
% ==============================================================================
\section{References}

\cvReference
    {Reference Name 1}
    {Title / Position}
    {Department Name}
    {Organization Name}
    {\href{mailto:email1@example.com}{email1@example.com} \\ +1 234 567 890}

\cvReference
    {Reference Name 2}
    {Title / Position}
    {Department Name}
    {Organization Name}
    {\href{mailto:email2@example.com}{email2@example.com} \\ +1 234 567 890}

\end{document}